Kids PM Summary

### 2020-01-13 moisture_data_cleaning.Rmd
data cleaning updates

---
title: "KidsAIR initial moisture content data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 13 Dec 2019"
output: pdf_document
---

@@

# Load, format, and save fuel moisture content data
```{r}
# Load data
moisture_initial_wmt <- read_xlsx("Input/wmt_kids_moisture_20191122.xlsx")

kids_moisture <- moisture_initial_wmt %>% 
  # rename variables
  mutate(moisture_id = as.factor(ID),  
         home_winter_id = as.factor(HomeWinterID),
         moisture_date = ymd(CompletedDate),
         moisture_1 = as.numeric(Moisture1),
         moisture_2 = as.numeric(Moisture2),
         moisture_3 = as.numeric(Moisture3),
         moisture_ave = as.numeric(MoistureAve),
         moisture_missing = as.character(WhatMissing),
         moisture_incomplete = as.factor(Incomplete),
         moisture_ignore_missing = as.factor(IgnoreMissingData),
         moisture_ignore_reason = as.character(IgnoreReason),
         moisture_tech = as.character(Technician),
         moisture_split = as.factor(Split),
         area = "WMT") %>% 
  # replace 0 and -999 values with NA
  replace_with_na(replace = list(moisture_1 = 0, moisture_2 = 0,
                                 moisture_3 = 0, moisture_ave = 0)) %>% 
  replace_with_na(replace = list(moisture_1 = -999, moisture_2 = -999,
                                 moisture_3 = -999)) %>% 
  # gather 3 moisture samples to calculate average
  gather("sample", "value", c("moisture_1":"moisture_3")) %>% 
  group_by(home_winter_id, moisture_date) %>% 
  mutate(moisture_ave = mean(value, na.rm = TRUE)) %>% 
  ungroup() %>% 
  # spread 3 moisture samples back to wide format
  spread(sample, value) %>% 
  select(moisture_id, home_winter_id, area, moisture_date, moisture_1, moisture_2, moisture_3, 
         moisture_ave, moisture_missing, moisture_incomplete, moisture_ignore_missing,
         moisture_ignore_reason, moisture_tech, moisture_split)

# Save as RDS and CSV
write_rds(kids_moisture, "Output/kids_moisture.rds")
write_csv(kids_moisture, "Output/kids_moisture.csv")
```

>>>>

---
title: "KidsAIR initial moisture content data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 13 Jan 2020"
output: pdf_document
---

@@

# Load, format, and save fuel moisture content data
```{r}
##### WMT #####
# Load data
moisture_initial_wmt <- read_xlsx("Input/WMT/wmt_kids_moisture_20191122.xlsx")

wmt_moisture <- moisture_initial_wmt %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         moisture_date = ymd(CompletedDate),
         moisture_1 = as.numeric(Moisture1),
         moisture_2 = as.numeric(Moisture2),
         moisture_3 = as.numeric(Moisture3),
         moisture_ave = as.numeric(MoistureAve),
         moisture_split = as.factor(Split),
         area = "WMT") %>% 
  # replace 0 and -999 values with NA
  replace_with_na(replace = list(moisture_1 = 0, moisture_2 = 0,
                                 moisture_3 = 0, moisture_ave = 0)) %>% 
  replace_with_na(replace = list(moisture_1 = -999, moisture_2 = -999,
                                 moisture_3 = -999)) %>% 
  # gather 3 moisture samples to calculate average
  gather("sample", "value", c("moisture_1":"moisture_3")) %>% 
  group_by(home_winter_id, moisture_date) %>% 
  mutate(moisture_ave = mean(value, na.rm = TRUE)) %>% 
  ungroup() %>% 
  # spread 3 moisture samples back to wide format
  spread(sample, value) %>% 
  select(home_winter_id, area, moisture_date, 
         moisture_1, moisture_2, moisture_3, 
         moisture_ave, moisture_split) %>% 
  arrange(home_winter_id, moisture_date)

# Save as RDS 
# write_rds(wmt_moisture, "Output/wmt_moisture.rds")

##### NN #####
# Load data
moisture_initial_nn <- read_xlsx("Input/NN/nn_moisture_20200113.xlsx")

nn_moisture <- moisture_initial_nn %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         moisture_date = ymd(CompletedDate),
         moisture_1 = as.numeric(Moisture1),
         moisture_2 = as.numeric(Moisture2),
         moisture_3 = as.numeric(Moisture3),
         moisture_ave = as.numeric(MoistureAve),
         moisture_split = as.factor(Split),
         area = "NN") %>% 
  # replace 0 and -999 values with NA
  replace_with_na(replace = list(moisture_1 = 0, moisture_2 = 0,
                                 moisture_3 = 0, moisture_ave = 0)) %>% 
  replace_with_na(replace = list(moisture_1 = -999, moisture_2 = -999,
                                 moisture_3 = -999)) %>% 
  # gather 3 moisture samples to calculate average
  gather("sample", "value", c("moisture_1":"moisture_3")) %>% 
  group_by(home_winter_id, moisture_date) %>% 
  mutate(moisture_ave = mean(value, na.rm = TRUE)) %>% 
  ungroup() %>% 
  # spread 3 moisture samples back to wide format
  spread(sample, value) %>% 
  select(home_winter_id, area, moisture_date, 
         moisture_1, moisture_2, moisture_3, 
         moisture_ave, moisture_split) %>% 
  arrange(home_winter_id, moisture_date)

# Save as RDS 
# write_rds(nn_moisture, "Output/nn_moisture.rds")

##### AK #####
# Load data
moisture_initial_ak <- read_xlsx("Input/AK/ak_moisture_20200113.xlsx")

ak_moisture <- moisture_initial_ak %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         moisture_date = ymd(CompletedDate),
         moisture_1 = as.numeric(Moisture1),
         moisture_2 = as.numeric(Moisture2),
         moisture_3 = as.numeric(Moisture3),
         moisture_ave = as.numeric(MoistureAve),
         moisture_split = as.factor(Split),
         area = "AK") %>% 
  # replace 0 and -999 values with NA
  replace_with_na(replace = list(moisture_1 = 0, moisture_2 = 0,
                                 moisture_3 = 0, moisture_ave = 0)) %>% 
  replace_with_na(replace = list(moisture_1 = -999, moisture_2 = -999,
                                 moisture_3 = -999)) %>% 
  # gather 3 moisture samples to calculate average
  gather("sample", "value", c("moisture_1":"moisture_3")) %>% 
  group_by(home_winter_id, moisture_date) %>% 
  mutate(moisture_ave = mean(value, na.rm = TRUE)) %>% 
  ungroup() %>% 
  # spread 3 moisture samples back to wide format
  spread(sample, value) %>% 
  select(home_winter_id, area, moisture_date, 
         moisture_1, moisture_2, moisture_3, 
         moisture_ave, moisture_split) %>% 
  arrange(home_winter_id, moisture_date)

# Save as RDS 
# write_rds(ak_moisture, "Output/ak_moisture.rds")
```

# Join moisture data from different areas
```{r}
wmt_moisture <- read_rds("Output/wmt_moisture.rds")
nn_moisture <- read_rds("Output/nn_moisture.rds")
ak_moisture <- read_rds("Output/ak_moisture.rds")

kids_moisture <- rbind(wmt_moisture, nn_moisture, ak_moisture)

# write_rds(kids_moisture, "Output/kids_moisture.rds")
```

# Clean up all moisture data
```{r}
kids_moisture <- read_rds("Output/kids_moisture.rds")

kids_moisture_clean <- kids_moisture

# write_rds(kids_moisture_clean, "Output/kids_moisture_clean.rds")
```

### 2020-01-13 pm_summary.Rmd
data cleaning updates

---
title: "Kids PM Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 19 Dec 2019"
output: pdf_document
---

@@

# Summary stats
```{r}
pm_summary <- kids_pm %>% 
  # group by: area, treatment, dtid, day_of_week, Sampling_day
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "Median PM" = median(pm, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "Mean Sample Obs" = mean(pm_total_observations, na.rm = TRUE),
            "Mean % Daily Obs" = mean(percent_daily_obs_pm, na.rm = TRUE))
```

>>>>

---
title: "Kids PM Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 13 Jan 2020"
output: pdf_document
---

@@

# Summary stats
```{r}
pm_summary <- kids_pm %>% 
  # group by: area, treatment, dtid, day_of_week, Sampling_day
  group_by(treatment) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "Median PM" = median(pm, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "Mean Sample Obs" = mean(pm_total_observations, na.rm = TRUE),
            "Mean % Daily Obs" = mean(percent_daily_obs_pm, na.rm = TRUE))
```
